Supporting Information

### 2021-11-04 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
update
rerun

dev.new()
png("q1_1_new.png", width = 1000, height = 1500)
p3
graphics.off()

@@

p7 <- ggarrange(p4,p5,p6, heights = c(1.1, 1, 0.7), ncol = 1, nrow = 3)

@@

![ROB Q1_1](q1_1_new.png)
![ROB Q1_1](q1_2_new.png)
![ROB Q1_1](q2_new.png)

>>>>

dev.new()
pdf("q1_1_new.pdf", width = 1000, height = 1500)
p3
graphics.off()

@@

p7 <- ggarrange(p4,p5,p6, heights = c(1, 0.8, 0.8), ncol = 1, nrow = 3)

@@

![ROB Q1_1](q1_1_new.pdf)
![ROB Q1_1](q1_2_new.png)
![ROB Q1_1](q2_new.png)
